Oriented Gradient Histogram applied to P300 Detection

### 2017-11-27 article.tex
cambios menores

On the generated image, a keypoint $\mathbf{kp}$ is placed on a pixel $(x_kp, y_kp)$ over the image plot. In Figure  \ref{fig:sampledescriptor}.  Around the keypoint, a local image patch is constructed by dividing it in 16 blocks of size $ 3 \cdot s $ where $ s is the size of the local patch $, arranged in a 4x4 grid and centered on $ \mathbf{kp} = (x_kp,y_kp)$, the patch center.

@@

\begin{figure}[H]
\centering
\includegraphics[width=5cm]{descriptorpatchsample.png}
\includegraphics[width=6cm]{histogramsbines.png}
%\includegraphics[width=9cm]{gradientszoom.png}
\caption{(Left) AGREGAR UN GRAFICO QUE MUESTRE MEJOR EL HISTOGRAMA Y PONER UNO DONDE EL P300 CON SU DESCRIPTOR SE VEAN PERFECTO.The local patch is located on a precise location within the generated plot. The 4x4 block grid can be seen on the patch. (Right) On each grid block, eight bins are used to describe the eight different orientations, and they are later arranged in a 128-dimension vector (4x4x8).}
\label{fig:sampledescriptor}
\end{figure}

>>>>

On the generated image, a keypoint $\mathbf{kp}$ is placed on a pixel $(x_{kp}, y_{kp})$ over the image plot. Figure~\ref{fig:sampledescriptor} shows a patch centered in the keypoint and.  Around the keypoint, a local image patch is constructed by dividing it in 16 blocks of size $ 3 \cdot s $ where $ s$ is the size of the local patch , arranged in a $4 \times 4$ grid and centered on $ \mathbf{kp} = (x_{kp},y_{kp})$, the patch center.

@@

\begin{figure}[H]
\centering
\subfigure{[The local patch]\includegraphics[width=5cm]{descriptorpatchsample.png}\label{patch}}
\subfigure[The local patch]{\includegraphics[width=6cm]{histogramsbines.png}\label{histogrambines}}
%\includegraphics[width=9cm]{gradientszoom.png}
\caption{(Left) AGREGAR UN GRAFICO QUE MUESTRE MEJOR EL HISTOGRAMA Y PONER UNO DONDE EL P300 CON SU DESCRIPTOR SE VEAN PERFECTO.The local patch is located on a precise location within the generated plot. The 4x4 block grid can be seen on the patch. (Right) On each grid block, eight bins are used to describe the eight different orientations, and they are later arranged in a 128-dimension vector (4x4x8).}
\label{fig:sampledescriptor}
\end{figure}
